A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-26 4_method.tex
new terminology figure
move beading strategy to toolpath extraction section
We don't need the toolpath locations L until that point.
remove section on rounding local maxima odd bead count because we don't do that any more
we dont do it anymore because it deviates from the core method too much and introduces all kinds of horrible edge cases

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/legend_double_wedge_example.pdf}
\caption{Explanation of terms.}
\label{legend}
\end{figure}

@@

If a local maximum gets an odd bead count this would result in a single dot bead toolpath with zero length.
This not only forms an exception we would need to account for when extracting toolpath segments,
it also results in a toolpath which is difficult to manufacture.
Instead we prevent odd bead counts by either increasing or decresing the bead count based on the prefered widths of those bead counts:
if $v.B^* \% 2 = 1$ then $v.B^* := \argmin_n |p(n) - R(v)|$.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
\caption{Explanation of terms.}
\label{legend}
\end{figure}

@@
